Visualization and analysis of probability distributions of large temporal data

### 2022-02-22 report/response.Rmd

> Q15. The last paragraph on p. 48 uses $<$ while equation (3.2) uses $\leqslant$. Which one is correct?

Done.
$\leqslant$ for both.

> Q16. Match the text on p. 50 and introduce the abbreviations from Figure 3.7 and Table 3.3, e.g., "hod" likely is "hour day" and so on. Introducing these abbreviations on p. 53 comes
too late.

Done.
Added the abbreviations on Page 50 in "Choosing cyclic granularities of interest and removing clashes" section.

@@

> Q17. In Figure 3.7a, it is not clear what the eight heatmaps represent. Do they belong to id 1, ..., id 8 ? Some explanation in the text or listing the id information on the left would be helpful. Similarly, on p. 53, the text states: id 7 and 8 have the same significant harmonies. I do not know where to look at the heatmaps in Figure 3.7a to find this information (and what is mentioned under items 2. and 3. in the text). Some explanation and labeling is
needed here.

discuss.

> Q18. How were the harmony pairs selected and sorted in Figure 3.7 and Table 3.3? headmaps show 25 pairs, the parallel coordinate plot shows only 14 (same as Table 3.3). However, the last two are sorted differently, "hod wdwnd" (the first row in the table) is neither the first nor the last row in the parallel coordinate plot.

CLARIFICATION 1: Each household is represented by 25 tiles, each tile representing a pair of cyclic granularities. The colors (in shades of red) represent the value of $wpd$ for each of the harmony pairs (in Table Table 3.3) and the grey tiles correspond to clashes. A darker shade of red corresponds to higher values of $wpd$.

CLARIFICATION 2: The harmony pairs in the parallel coordinate plot are arranged from highest to lowest values of $wpd$ averaged over all households and hence do not correspond to the first or last rows of Table 3.3.

Changed the text description of Figure 3.7.

### 2022-02-23 report/response.Rmd

> Q8. Maybe include a reference for gestalt theory.

Added.
@wertheimer1938gestalt

> Q9. In Section 3.2.2, I find the references to the null distribution confusing. Surely that is the design in
Figure 3.3(a) only?

CLARIFICATION: Null distributions refer to the case when there is no significant distributional differences between categories of one or more granularities. Data in Fig 3.3 (a) is consistent with the null distribution.

> Q10. In table 3.1 $N_c$ is the number of cyclic granularities, whereas in the text (first sentence of 3.3.2 and
3.3.3) it is m.

@@

> Q13. I like Figure 3.4. In (3), the dotted arcs only connect to a1 which might be misleading.

Done.
Caption changed to incorporate that.
Within-facet distances are illustrated in Panels 3) (when categories are un-ordered, shown only with respect to a1) and Panel 4) (when categories are ordered)

> Q14. In the pairwise distance measure on page 43, is there any adjustment made for varying numbers of observations across the levels of A and B? For example in Figure 3.3(d) if there are few values at xlevel=1 the comparison shown is less interesting

CLARIFICATION: As long as that there is enough data for each level or combination of levels, no adjustment for varying number of observations is done. If there are few data for one or more levels, subsequent categories could be collapsed to obtain precise estimates of quantiles.

Added under the subsection "Characterizing distributions".

@@

> Q15. The equations on page 44 could be tidied up. There are extra () on the definition of wpdperm and on the residual definition at the bottom of the page. Use $\times$ for the equations.

Done.

> Q16. Is there a practical reason why $wpd_{glm}$ is not working as expected for lower nx and nf?

CLARIFICATION: There is no practical explanation for this, but a more empirical one - with smaller $n_x$ and $n_f$, the variance in the values of $wpd_{raw}$ is greater. As a result, our modeling technique that attempts to fit $wpd_{raw}$ to the number of comparisons ($n_x\times n_f$) performs poorly. The increased volatility in the values of $wpd_{raw}$ with a smaller number of levels is due to the fact that no asymptotic distribution for the statistic "maximum" (which is the foundation of $wpd_{raw}$) across such small number of values could be produced.

@@

> Q13. The Results section and Figure 3.5 need some clarifications. The text states: Figure 3.5 shows that both the location and scale of the distributions change across panels. I suppose this figure relates to m = 2, but this is not stated in the main text. Table 3.2 lists both, m = 1 and m = 2. Moreover, in Figure 3.5, the y-axis ticmark labels overplot and the nx values are partially cut off.

Done.
We decided to remove the y-axis labels in the interest of space. The y-axis is showing the density values but we are only interested in its shape.

CLARIFICATION: Added $m=2$ in the caption of Figures 3.5 and 3.6.

> Q14. There are similar problems with the labels in Figure 3.6. Moreover, the two overlaid curves are very hard to distinguish. Would it help to change colors and transparency, or draw the boundary of the curves with the specific colors (and not in black)? This may require some experimentation. Finally, using a differently colored background (say light yellow) would be helpful to visually demonstrate where $wpd_{perm}$ is being used. For the legend, use the terms as in equation (3.2) and not the full word.

Done. Changed to make it more clear than earlier.

### 2022-02-23 Rmd/03-hakear.Rmd
Catherine Q9,14,16 Ch3

Multiple observations of $v$ correspond to the subset $v_{jk} = \{s: A(s) = j, B(s) = k\}$. The number of observations might vary widely across subsets due to the structure of the calendar, missing observations or uneven locations of events in the time domain. In this paper, quantiles of $\{v_{jk}\}$ are chosen as a way to characterize distributions for the category $(a_j, b_k)$, $\forall j\in \{1, 2, \dots, \nx\}, k\in \{1, 2, \dots, \nf\}$. We use percentiles with $p = {0.01, 0.02, \dots, 0.99}$ to reduce the computational burden in summarizing distributions.

>>>>

Multiple observations of $v$ correspond to the subset $v_{jk} = \{s: A(s) = j, B(s) = k\}$. The number of observations might vary widely across subsets due to the structure of the calendar, missing observations or uneven locations of events in the time domain. In this paper, quantiles of $\{v_{jk}\}$ are chosen as a way to characterize distributions for the category $(a_j, b_k)$, $\forall j\in \{1, 2, \dots, \nx\}, k\in \{1, 2, \dots, \nf\}$. We use percentiles with $p = {0.01, 0.02, \dots, 0.99}$ to reduce the computational burden in summarizing distributions. The assumption is that there is sufficient data for each level or combination of levels, and hence no adjustment is made for the varying number of observations across levels. However, if one or more levels has a small number of data points, consecutive categories should be collapsed prior to data transformation and quantile estimation.
